CODECHECK: An open-science initiative for the independent execution of computations underlying research articles.

### 2021-01-07 codecheck-paper.tex
this version is good enough to send out for comment/checking acks

\begin{enumerate}
\item Check with Giuliano re: ``code works''. Write to Naomi.
\item Can we introduce "research compendium" as a term?  (yes).
\item Should we make code and data sharing a prerequisite or leave
  that door open? (make it the norm)
\item Take a look at the Lancet's statistical review process (areas for improvement by authors) \url{https://www.thelancet.com/journals/lancet/article/PII0140-6736(92)90409-V/fulltext}
\item How to relate to "reproducibility does not matter but trust does", see \url{https://gmbecker.github.io/MayInstituteKeynote2019/outline.html}
\item Check with people  in the acknowledgements
%\item revisit \url{https://github.com/codecheckers/discussion}
% \item \url{https://hdsr.mitpress.mit.edu/pub/f0obb31j/release/1} and other articles form the HDSR special issue
% \item \url{https://av.tib.eu/media/42484} > "Code will make systematic mistakes, not random mistakes", "code is more reliable (and auditable) than a human"
\end{enumerate}

>>>>

\begin{enumerate}
\item Check with Giuliano re: ``code works''. Write to Naomi.
\item Can we introduce "research compendium" as a term?  (yes).
\item Should we make code and data sharing a prerequisite or leave
  that door open? (make it the norm)
% \item How to relate to "reproducibility does not matter but trust does", see \url{https://gmbecker.github.io/MayInstituteKeynote2019/outline.html}
\item Check people  are okay being listed in acknowledgements
%\item revisit \url{https://github.com/codecheckers/discussion}
% \item \url{https://hdsr.mitpress.mit.edu/pub/f0obb31j/release/1} and other articles form the HDSR special issue
% \item \url{https://av.tib.eu/media/42484} > "Code will make
% systematic mistakes, not random mistakes", "code is more reliable
% (and auditable) than a human"
% \item Take a look at the Lancet's statistical review process (areas for improvement by authors) \url{https://www.thelancet.com/journals/lancet/article/PII0140-6736(92)90409-V/fulltext}

\end{enumerate}
